\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2014-04-01 introduction.tex
Updated paper

Reactive languages~\cite{gber931,amal10} are a class of programming
languages used for designing and implementing reactive systems, which
continuously respond to input from their environment. These languages
have been successfully used in programming a plethora of systems such as
fly-by-wire in Airbus~\cite{eairbus}, security surveillance
systems~\cite{amal121}, etc. Usually these systems also need to meet
real-time constraints imposed by the environment. Yet, these languages
do not support describing real-time statements as first class language
constructs.  For example, one cannot describe a simple real-time delay
(postponement) of an operation for 0.2 ms. These languages are based on
formal semantics, essential for correct by construction code generation
and formally verifying functional properties of developed programs, but
leave nonfunctional properties such as timing behavior as an
implementation detail~\cite{boldt07}. Arguably, rightly so, because
physical time cannot be incorporated without information about the
underlying execution platform.  But, one can still reason in terms of
logical time. These languages support discrete logical clock rather than
a discrete physical (real-time) clock. The real-time period of the
discrete logical clock (also referred to as a logical tick) is not fixed
and it is determined by the speed of computation of the program for
different input signals. Unlike a discrete physical clock, which has
fixed real-time period, the period of the logical clock is elastic.
Although the timing model with logical clock has worked well for
reactive synchronous/GALS languages in designing discrete systems, there
is a need to introduce real-time since often, implementation models are
in the continuous or discrete real-time
domain~\cite{DBLP:journals/pieee/SifakisTY03}. This paper targets
enhancing the expressiveness of formal GALS and synchronous languages by
adding real-time constructs. The real-time constructs speed up the
design process by allowing system designers to explicitly program
real-time control logic within the language itself without relying on
external resources such as timers.

@@

All aforementioned contributions hold under a single assumption that
real-time analyzable platforms are available. The rest of the paper is
arranged as follows: Section~\ref{sec:background} gives the background
on SystemJ and related techniques required for the rest of the paper.
Section~\ref{sec:intr-real-time} introduces real-time mechanisms in the
GALS paradigm and describes their compilation into logical time.
Section~\ref{sec:proof-correctness} sketches the correctness proofs for
the introduced algorithms. Section~\ref{sec:experimental-results} gives
the experimental results for a set of real-time applications. In
Section~\ref{sec:disc-perc-limit} we discuss the advantages and
limitations of the proposed approach. Section~\ref{sec:related-work}
positions this work in relation to other approaches to introducing
real-time in other languages. Finally, we conclude in
Section~\ref{sec:concl-future-work}.

>>>>

Reactive languages~\cite{gber931,amal10} are a class of programming
languages used for designing and implementing reactive systems, which
continuously respond to input from their environment. These languages
have been successfully used in programming a plethora of systems such as
fly-by-wire in Airbus~\cite{eairbus}, security surveillance
systems~\cite{amal121}, etc. Usually these systems also need to meet
real-time constraints imposed by the environment. Yet, these languages
do not support describing real-time statements as first class language
constructs.  For example, one cannot describe a simple real-time delay
(postponement) of an operation for 0.2 ms. These languages are based on
formal semantics, essential for correct by construction code generation
and formally verifying functional properties of developed programs, but
leave nonfunctional properties such as timing behavior as an
implementation detail~\cite{boldt07}. Arguably, rightly so, because
physical time cannot be incorporated without information about the
underlying execution platform.  But, one can still reason in terms of
logical time. These languages support discrete logical clock rather than
a discrete physical (real-time) clock. The real-time period of the
discrete logical clock (also referred to as a logical tick) is not fixed
and it is determined by the speed of computation of the program for
different input signals. Unlike a discrete physical clock, which has
fixed real-time period, the period of the logical clock is elastic.
Although the timing model with logical clock has worked well for
reactive synchronous/GALS languages in designing discrete systems, there
is a need to introduce real-time since often, implementation models are
in the continuous or discrete real-time
domain~\cite{DBLP:journals/pieee/SifakisTY03}. This paper targets
enhancing the expressiveness of formal GALS and synchronous languages by
adding real-time constructs. These real-time constructs speed up the
design process by allowing system designers to explicitly program
real-time control logic within the language itself without relying on
external resources such as timers. Introduction of real-time as a
language construct allows verification of temporal properties of
programs before deployment.

@@

All aforementioned contributions require a single \textbf{assumption}
that real-time analyzable platforms are available that allow computing
the timing bounds of SystemJ programs. This assumption is necessary for
all hard real-time system implementations~\cite{wilhelm08}.

The rest of the paper is arranged as follows:
Section~\ref{sec:background} gives the background on SystemJ and related
techniques required for the rest of the paper.
Section~\ref{sec:intr-real-time} introduces real-time mechanisms in the
GALS paradigm and describes their compilation into logical time.
Section~\ref{sec:proof-correctness} sketches the correctness proofs for
the introduced algorithms. Section~\ref{sec:experimental-results} gives
the experimental results for a set of real-time applications. In
Section~\ref{sec:disc-perc-limit} we discuss the advantages and
limitations of the proposed approach. Section~\ref{sec:related-work}
positions this work in relation to other approaches to introducing
real-time in other languages. Finally, we conclude in
Section~\ref{sec:concl-future-work}.
